```{r}

#libpath<-"/user_data/kalinka/r_packages"
#.libPaths(c(libpath, .libPaths()))
#remotes::install_github("MadsAlbertsen/ampvis2")
#install.packages("cowplot")
library(ampvis2)
library(cowplot)
library(vroom)
library(tidyverse)






```

####### And then trying with the new metadata ######


```{r}
otutable <-vroom("/user_data/kalinka/GraftM/shallow_21_12_2022/combined_count_table_pmoA.txt", delim = "\t")
otutable <- otutable %>%
rename(OTU = ConsensusLineage)

metadata <- readRDS("/projects/microflora_danica/Data_freezes/2022_10_10/2022-12-05_mfd-metadata.rds")
metadata <- metadata %>%
  rename(SeqId = seq_id) %>%
    relocate(SeqId) %>%
  filter(after_total_reads > 4000000) %>% #Filtering at 4 million paired end reads
  drop_na(mfd_sampletype)


```

Importing taxonomy file and renameing the OTU-file
```{r}

taxonomy <- data.frame(matrix(ncol = 8, nrow = 37))
x <- c("OTU","Kingdom", "Phylum", "Class","Order", "Family", "Genus", "Species")
colnames(taxonomy) <- x
taxonomy$OTU<-otutable$OTU
taxonomy <- taxonomy %>%
separate(OTU, into = c("Kingdom", "Phylum", "Class","Order", "Family", "Genus", "Species"), sep = '; ', remove=FALSE)
taxonomy$Species<-taxonomy$OTU


#And a little trick to make species look like OTU-level;
```


```{r}
d <- amp_load(otutable = otutable, metadata = metadata, taxonomy = taxonomy)

saveRDS(d, file = "/user_data/kalinka/GraftM/shallow_21_12_2022/amp_pmoA_new_meta.rds")

```


And perhaps 1 big pca

```{r}

d_s <- amp_subset_samples(d,
  mfd_sampletype %in% c("Sediment", "Soil" ))


pca2<- amp_ordinate(data = d_s, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_areatype",
            sample_shape_by = "mfd_sampletype",
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="GraftM package with contigs - New metadata")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))

pca2

 ggsave("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/pca_pmoA_new_graft_new_meta_24_01_23.png",
       pca2,
        height = 5,
  width = 10)

```

#### Okay and now to some filtering steps. I want to compare when I filter both the old and new data ######
```{r}
d_new<-readRDS("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/amp_pmoA_new_meta.rds")
d_old <-readRDS("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/amp_pmoA_old_graft_new_meta.rds")


d_new$tax <- d_new$tax %>%
  mutate(Species = if_else(Species == "Root", "Root_remove", Species))%>%
  mutate(Genus = str_extract(OTU, "[^;]*$")) ###Just for easy plotting at "genus = last word" level

d_old$tax <- d_old$tax %>%
  mutate(Species = if_else(Species == "Root", "Root_remove", Species))%>%
  mutate(Genus = str_extract(OTU, "[^;]*$")) ###Just for easy plotting at "genus = last word" level


tax_vector_new <- c("Root_remove","amoA", "Nitrospira", "Homologous_pmoA","Nitrosococcus", "Actinobacteria", "Root; pmoA_amoA_pxmA; pmoA", "Probably_hydrocarbon_monooxygenases", "Cycloclasticus", "Root; pmoA_amoA_pxmA; pxmA", "Root; pmoA_amoA_pxmA")

f_new <- amp_subset_taxa(d_new, tax_vector = tax_vector_new, remove = TRUE, normalise = TRUE)
x<-f_new$tax

tax_vector_old<-c("Root; pmoA_amoA_pxmA_umbrella; pxmA_amoA; pxmA","Rhodobacter_cluster","Root; pmoA_amoA_pxmA_umbrella","Root; pmoA_amoA_pxmA_umbrella; pmoA","Cycloclasticus_bradhyrhizobium_cluster","Root_remove","Total_Count", "HMO_cluster", "amoA", "Betaproteobacteria_amoA", "Actinobacteria", "Cycloclasticus", "Nitrosococcus", "Nitrospira_clade_A", "Nitrospira_clade_B")
f_old <- amp_subset_taxa(d_old, tax_vector = tax_vector_old, remove = TRUE, normalise = TRUE)
x<-f_old$tax

```

Og så til et lille plot
```{r}

f_new <- amp_subset_samples(f_new,
  mfd_sampletype %in% c("Sediment", "Soil" ))

f_old <- amp_subset_samples(f_old,
  mfd_sampletype %in% c("Sediment", "Soil" ))

pca_f_new<- amp_ordinate(data = f_new, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_areatype",
            sample_shape_by = "mfd_sampletype",
            species_plot = TRUE,
           species_nlabels = 10,
           species_label_taxonomy = "Genus",
           species_label_size = 4,
           species_label_color = "black",
           species_rescale = TRUE,
           filter_species=0,
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="GraftM package with contigs - New metadata and filtered")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))

pca_f_old<- amp_ordinate(data = f_old, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_areatype",
            sample_shape_by = "mfd_sampletype",
            species_plot = TRUE,
           species_nlabels = 10,
           species_label_taxonomy = "Genus",
           species_label_size = 4,
           species_label_color = "black",
           species_rescale = TRUE,
           filter_species=0,
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="Old GraftM package - New metadata and filtered")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))

p<-plot_grid(pca_f_new, pca_f_old, ncol = 2)

 ggsave("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/pca_old_and_new_with_filter.png",
       p,
        height = 6,
  width = 18)
```



What is happening to the agriculture???
```{r}

d_new<-readRDS("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/amp_pmoA_new_meta.rds")
d_old <-readRDS("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/amp_pmoA_old_graft_new_meta.rds")

d_old$tax <- d_old$tax %>%
  mutate(Genus = str_extract(OTU, "[^;]*$")) ###Just for easy plotting at "genus = last word" level

d_new$tax <- d_new$tax %>%
  mutate(Genus = str_extract(OTU, "[^;]*$")) ###Just for easy plotting at "genus = last word" level



a_new <- amp_subset_samples(d_new,
  mfd_areatype %in% "Agriculture")

a_old <- amp_subset_samples(d_old,
  mfd_areatype %in% "Agriculture")


pca_a_new<- amp_ordinate(data = a_new, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_hab2",
            sample_shape_by = "mfd_hab1",
            species_plot = TRUE,
           species_nlabels = 10,
           species_label_taxonomy = "Genus",
           species_label_size = 4,
           species_label_color = "black",
           species_rescale = TRUE,
           filter_species=0,
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="GraftM package with contigs - Agriculture")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))


pca_a_new

pca_a_old<- amp_ordinate(data = a_old, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_hab2",
            sample_shape_by = "mfd_hab1",
            species_plot = TRUE,
           species_nlabels = 10,
           species_label_taxonomy = "Genus",
           species_label_size = 4,
           species_label_color = "black",
           species_rescale = TRUE,
           filter_species=0,
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="Old GraftM package - Agriculture")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))

p<-plot_grid(pca_a_new, pca_a_old, ncol = 2)
p
 ggsave("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/pca_agriculture_no_filter.png",
       p,
        height = 6,
  width = 18)




af_new <- amp_subset_samples(f_new,
  mfd_areatype %in% "Agriculture")

af_old <- amp_subset_samples(f_old,
  mfd_areatype %in% "Agriculture")


pca_af_new<- amp_ordinate(data = af_new, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_hab2",
            sample_shape_by = "mfd_hab1",
            species_plot = TRUE,
           species_nlabels = 10,
           species_label_taxonomy = "Genus",
           species_label_size = 4,
           species_label_color = "black",
           species_rescale = TRUE,
           filter_species=0,
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="GraftM package with contigs - Agriculture after filter")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))


pca_af_new

pca_af_old<- amp_ordinate(data = af_old, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_hab2",
            sample_shape_by = "mfd_hab1",
            species_plot = TRUE,
           species_nlabels = 10,
           species_label_taxonomy = "Genus",
           species_label_size = 4,
           species_label_color = "black",
           species_rescale = TRUE,
           filter_species=0,
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="Old GraftM package - Agriculture after filter")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))

p<-plot_grid(pca_af_new, pca_af_old, ncol = 2)

 ggsave("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/pca_agriculture_after_filter.png",
       p,
        height = 6,
  width = 18)




##### Removed samples subset ######


d_new$tax <- d_new$tax %>%
  mutate(Species = if_else(Species == "Root", "Root_remove", Species))%>%
  mutate(Genus = str_extract(OTU, "[^;]*$")) ###Just for easy plotting at "genus = last word" level

d_old$tax <- d_old$tax %>%
  mutate(Species = if_else(Species == "Root", "Root_remove", Species))%>%
  mutate(Genus = str_extract(OTU, "[^;]*$")) ###Just for easy plotting at "genus = last word" level


tax_vector_new <- c("Root_remove","amoA", "Nitrospira", "Homologous_pmoA","Nitrosococcus", "Actinobacteria", "Root; pmoA_amoA_pxmA; pmoA", "Probably_hydrocarbon_monooxygenases", "Cycloclasticus", "Root; pmoA_amoA_pxmA; pxmA", "Root; pmoA_amoA_pxmA")
f_new_removed <- amp_subset_taxa(d_new, tax_vector = tax_vector_new, remove = FALSE, normalise = TRUE)

tax_vector_old<-c("Root; pmoA_amoA_pxmA_umbrella; pxmA_amoA; pxmA","Rhodobacter_cluster","Root; pmoA_amoA_pxmA_umbrella","Root; pmoA_amoA_pxmA_umbrella; pmoA","Cycloclasticus_bradhyrhizobium_cluster","Root_remove","Total_Count", "HMO_cluster", "amoA", "Betaproteobacteria_amoA", "Actinobacteria", "Cycloclasticus", "Nitrosococcus", "Nitrospira_clade_A", "Nitrospira_clade_B")
f_old_removed <- amp_subset_taxa(d_old, tax_vector = tax_vector_old, remove = FALSE, normalise = TRUE)

r_new <- amp_subset_samples(f_new_removed,
  mfd_areatype %in% "Agriculture")

r_old <- amp_subset_samples(f_old_removed,
  mfd_areatype %in% "Agriculture")

pca_r_new<- amp_ordinate(data = r_new, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_hab2",
            sample_shape_by = "mfd_hab1",
            species_plot = TRUE,
           species_nlabels = 10,
           species_label_taxonomy = "Genus",
           species_label_size = 4,
           species_label_color = "black",
           species_rescale = TRUE,
           filter_species=0,
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="GraftM package with contigs - Agriculture removed samples")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))


pca_r_old<- amp_ordinate(data = r_old, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "mfd_hab2",
            sample_shape_by = "mfd_hab1",
            species_plot = TRUE,
           species_nlabels = 10,
           species_label_taxonomy = "Genus",
           species_label_size = 4,
           species_label_color = "black",
           species_rescale = TRUE,
           filter_species=0,
            size=10) +
  scale_color_manual(values=c("#69d44f", "#ce1515", "#eed70d",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#01b5b7",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="Old GraftM package - Agriculture removed")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))

p<-plot_grid(pca_r_new, pca_r_old, ncol = 2)

 ggsave("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/pca_agriculture_removed.png",
       p,
        height = 6,
  width = 18)

### Heatmaps of the removed samples ####

## Using the all_subset just to see the difference in what is picked up between the two

a_new <- amp_subset_samples(f_new_removed,
  mfd_areatype %in% "Agriculture",  normalise = TRUE,  removeAbsentOTUs = TRUE )

r_old <- amp_subset_samples(f_old_removed,
  mfd_areatype %in% "Agriculture")


a_new <- amp_subset_samples(d_new,
  mfd_areatype %in% "Agriculture",  normalise = TRUE,  removeAbsentOTUs = TRUE)

a_old <- amp_subset_samples(d_old,
  mfd_areatype %in% "Agriculture",  normalise = TRUE,  removeAbsentOTUs = TRUE)


hm_r_new <- amp_heatmap(a_new,
 facet_by = "mfd_sampletype",
 group_by = "mfd_areatype",
 tax_aggregate = "Genus",
 tax_show = 18,
 color_vector = c("white", "darkred"),
 plot_colorscale = "sqrt",
 plot_values = TRUE,
 plot_values_size = 2.5) +
theme(axis.text.x = element_text(angle = 45, size=8, vjust = 1),
 axis.text.y = element_text(size=8),
  legend.position="right")

hm_r_new

hm_a_old <- amp_heatmap(af_old,
  facet_by = "mfd_hab1",
 group_by = "mfd_hab2",
 tax_aggregate = "Genus",
 tax_show = 18,
 color_vector = c("white", "darkred"),
 plot_colorscale = "sqrt",
 plot_values = TRUE,
 plot_values_size = 2.5) +
theme(axis.text.x = element_text(angle = 45, size=8, vjust = 1),
 axis.text.y = element_text(size=8),
  legend.position="right")

hm_a_old

```





################## With the old metadata #################

```{r}
otutable <-vroom("/user_data/kalinka/GraftM/shallow_21_12_2022/combined_count_table_pmoA.txt", delim = "\t")
otutable <- otutable %>%
rename(OTU = ConsensusLineage)

metadata <- read.delim("/projects/microflora_danica/Data_freezes/2022_09_08/2022-07-26_mfd_minimal_metadata.txt", header = TRUE, sep = " ") # nolint
metadata <- metadata %>%
  separate(gps_location, into = c("latitude","longitude"), sep = ',') %>%
  rename(SeqId = seq_id) %>%
    drop_na(after_total_reads) %>%
    relocate(SeqId) %>%
  filter(after_total_reads > 4000000)


```

Importing taxonomy file and renameing the OTU-file
```{r}
taxonomy <- read.delim("/user_data/kalinka/GraftM/combining_out/pmoA_taxonomy.csv", header = TRUE, sep = ",")
otutable$OTU<-taxonomy$OTU

taxonomy <- data.frame(matrix(ncol = 8, nrow = 37))
x <- c("OTU","Kingdom", "Phylum", "Class","Order", "Family", "Genus", "Species")
colnames(taxonomy) <- x
taxonomy$OTU<-otutable$OTU
taxonomy <- taxonomy %>%
separate(OTU, into = c("Kingdom", "Phylum", "Class","Order", "Family", "Genus", "Species"), sep = '; ', remove=FALSE)
taxonomy$Species<-taxonomy$OTU


#And a little trick to make species look like OTU-level;
```

```{r}
d <- amp_load(otutable = otutable, metadata = metadata, taxonomy = taxonomy)

saveRDS(d, file = "/user_data/kalinka/GraftM/shallow_21_12_2022/amp_pmoA_old_meta.rds")
#stats <- amp_alphadiv(data = d)

#amp_rarecurve(data = d, 
 #             color_by = "sample_type", 
  #            stepsize = 10) + 
   #           xlim(0, 900)

```


```{r}

pca_habitat<- amp_ordinate(data = d, 
             type = "PCA", 
             transform = "hellinger", 
             sample_color_by = "habitat_type")
            #sample_colorframe = TRUE)

pca_habitat

ggsave("/user_data/kalinka/metadata/pca_habitat.png",
       pca_habitat,
       height = 10,
       width = 10)

```


```{r}
heatmap_habitat<-amp_heatmap(d,
  group_by = "habitat_type",
  tax_aggregate = "Species",
  tax_show = 25,
  facet="habitat_type")+  
  theme(axis.text.x=element_blank(), axis.text.y = element_text(size = 9),
                    axis.ticks.x=element_blank())

ggsave("/user_data/kalinka/metadata/heatmap_habitat.png",
       heatmap_habitat,
       height = 8,
       width = 20)
```


New heatmap

```{r}

d_s <- amp_subset_samples(d,
  sample_type %in% c("sediment", "soil" ))

tax_vector<-c("Root_pmoA","Actinobacteria", "HMO_cluster")
d_no_root <- amp_subset_taxa(d_s, tax_vector = tax_vector, remove = TRUE)
  
heatmap2 <- amp_heatmap(d_s,
  facet_by = "sample_type",
 group_by = "habitat_type",
 tax_aggregate = "Species",
 tax_show = 32,
 color_vector = c("white", "darkred"),
 plot_colorscale = "sqrt",
 plot_values = TRUE,
 plot_values_size = 2.5) +
theme(axis.text.x = element_text(angle = 45, size=8, vjust = 1),
 axis.text.y = element_text(size=8),
  legend.position="right")

ggsave("/user_data/kalinka/metadata/heatmap2_pmoA.png",
       heatmap2,
       height = 9,
       width = 9)


heatmap2_no_root <- amp_heatmap(d_no_root,
  facet_by = "sample_type",
 group_by = "habitat_type",
 tax_aggregate = "Species",
 tax_show = 27,
 color_vector = c("white", "darkred"),
 plot_colorscale = "sqrt",
 plot_values = TRUE,
 plot_values_size = 2.5) +
theme(axis.text.x = element_text(angle = 45, size=8, vjust = 1),
 axis.text.y = element_text(size=8),
  legend.position="right")

ggsave("/user_data/kalinka/metadata/heatmap2_no_root_pmoA.png",
       heatmap2_no_root,
       height = 9,
       width = 9)

```


And some PCA stuff

```{r}

sediment_subset <- amp_subset_samples(d,
  sample_type %in% "sediment")

soil_subset <- amp_subset_samples(d,
   sample_type %in% "soil")

pca_soil<- amp_ordinate(data = soil_subset, 
       type = "PCA", 
           transform = "hellinger", 
           sample_color_by = "habitat_type")
pca_sediment<- amp_ordinate(data = sediment_subset, 
             type = "PCA", 
             transform = "hellinger", 

             sample_color_by = "habitat_type")


ggsave("/user_data/kalinka/metadata/pcasoil.png",
        pca_soil,
        height = 7,
        width = 8)
 ggsave("/user_data/kalinka/metadata/pcasediment.png",
       pca_sediment,
        pca_sediment,
        height = 7,
  width = 8)
```


And perhaps 1 big pca

```{r}
pca2<- amp_ordinate(data = d_s, 
            type = "PCA", 
             transform = "hellinger", 
            sample_color_by = "habitat_type",
            sample_shape_by = "sample_type",
            size=10) +
  scale_color_manual(values=c("#69d44f",
"#1f0060",
"#00c18d",
"#ec60c0",
"#004563",
"#8773ea",
"#d45828",
"#0092f3",
"#ce1515",
"#01b5b7",
"#eed70d",
"#dec7b0",
"#1d0b00"), name = "Habitat")+
scale_shape_discrete(name="Sample Type")+
  labs(title="GraftM package with contigs - Old metadata")+
  theme(plot.title = element_text(hjust=0.5, face="bold"))

pca2

 ggsave("/user_data/kalinka/GraftM/shallow_21_12_2022/R_scripts_and_figures/pca_pmoA_new_graft_old_meta_24_01_23.png",
       pca2,
        height = 5,
  width = 10)

```





Diversity
```{r}

tax_vector<-c("Total_Count", "HMO_cluster", "Root_pmoA", "amoA", "Betaproteobacteria_amoA", "Actinobacteria", "Cycloclasticus", "Nitrosococcus", "Nitrospira_clade_A", "Nitrospira_clade_B")

d_positives <- amp_subset_taxa(d, tax_vector = tax_vector, remove = TRUE, normalise = TRUE)

alphadiversityresult <- amp_alphadiv(d_positives,
  measure = c("observed","shannon"))


alphadiversityresult_subset<-alphadiversityresult%>%
filter(Shannon>2 & Reads>60) 



#Maybe I can make a new ampvis_element form this?

diversity_ampvis <- amp_load(otutable = otutable, metadata = alphadiversityresult_subset, taxonomy = taxonomy)
tax_vector<-c("Total_Count", "HMO_cluster", "Root_pmoA", "amoA", "Betaproteobacteria_amoA", "Actinobacteria", "Cycloclasticus", "Nitrosococcus", "Nitrospira_clade_A", "Nitrospira_clade_B")

diversity_ampvis <- amp_subset_taxa(diversity_ampvis, tax_vector = tax_vector, remove = TRUE, normalise = TRUE)

#That worked! Now to a little heatmap!



heatmap_diverse_samples <- amp_heatmap(diversity_ampvis,
  facet_by = "habitat_type",
 group_by = "fieldsample_barcode",
 tax_aggregate = "Species",
 tax_show = 27,
 color_vector = c("white", "darkred"),
 plot_colorscale = "sqrt",
 plot_values = TRUE,
 plot_values_size = 2.5) +
theme(axis.text.x = element_text(angle = 45, size=8, vjust = 1),
 axis.text.y = element_text(size=8),
  legend.position="right")

heatmap_diverse_samples

ggsave("/user_data/kalinka/metadata/diverse.png",
       heatmap_diverse_samples,
        height = 8,
  width = 30)


```

